On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-14 response.tex

\documentclass{article}

\setlength\textheight{19.5cm}

\newcommand{\comment}[1]{\vspace{1em} \emph{#1} \vspace{1em}}

\begin{document}

\section{Reviewer 1}

...

In the footer on the first page, please add a concise statement of
the paper's addition after "This paper is a revised and extended
version of [Turpin et al. 2015]; it adds XXX." By the way, you
should use [Author year] when you refer to a publication and Author
[year] when you refer to the author (citep{xxx} and citet{xxx},
respectively).

\comment{This has been fixed, thank you.}

In the related work section, please make precise how the TOIS
submission differs from the earlier SIGIR 2015 paper.

\comment{A paragraph has been added at the end of Section 2.1 to do this.}

RQ2 is an important additional ingredient of this extended paper.
Section 6 is devoted to answering this question. Please explicitly
announce that that is what you are going to do. And please provide
answers to the question at the end of section 6. We are now left
to discover for ourselves what (if any) answer you were able to
produce for RQ2.

\comment{to do }

\noindent ...

\section{Reviewer 2}

I like the paper and the problem that it addresses: magnitude
estimation for information retrieval and the use of crowd sourcing
for this purpose. The authors claim that their findings are direct
implications for IR evaluation. This is probably true, but I think
the authors can do a better job of articulating them. I recommend
that each result section 5-8 explicitly (1) starts with one of the
four research questions, (2) answers it, (3) explains what the
ramifications of the answers are for IR evaluation.

\comment {todo}

Some more specific comments:

Section 2.3: good addition. You could consider adding a brief
discussion on the value of crowd worker disagreement. There is work
by Lora Aroyo and Chris Welty that you should probably relate to
in section 2.3

\comment {todo}

Section 4: This is a better way of organizing the material than in
the SIGIR version. Collect and report on the data first. And only
interpret and conclude later. Moving bits from section 3 here (on
crowd judging and score normalization) makes good sense. Figures 1
and 2 are new. And so is section 4.2; adding a sentence to 4.2 with
the upshot of the section would be useful. The expansion of 4.3
(formerly 3.3) is useful.

\comment {We have added the sentence at the end of 4.2}

The new section 5 coincides more  or less with section 4 in the
SIGIR paper. Is "We therefore next investigate judge agreement"
still a useful  way of ending this section, given the inclusion of
a new research question?

\comment {We have deleted the offending sentence at the end of Section 5.}

Section 6:  ranges of scores for each worker involved was very wide
--> RANGE of scores. Figure 7 has no legends (neither x nor y).
What are the practical implications of the statement at the very
end of section 6, about the number of required workers? And what
does it say about setups where a smaller number of workers has been
used?

\comment {to do}

Section 7 coincides with the old section 5. Figs 10, 11, 12 need
legends. It would be good to explain the differences in absolute
numbers between Table IV in the TOIS submission and Table 2 in the
SIGIR paper. And why these differences do not matter.

\comment {to do}

Section 8: I am not sure I am happy with the uncertain ending of
this section. What does the disagreement with Kanoulas and Aslam's
earlier work mean for our "ideal" evaluation setup?

\comment {to do}

Section 9: the addition of a "limitations" section is an excellent
idea.

Appendix A: I like this addition. A screen dump of the instruction
interface would have been helpful.

\comment {to do}

\end{document}

### 2016-09-14 response.tex

\documentclass{article}

\usepackage{xcolor}
\usepackage[top=10mm, bottom=10mm, left=10mm, right=10mm]{geometry}

\newcommand{\comment}[1]{\vspace{1em} \textcolor{red}{{#1}} \vspace{1em}}

@@

\comment {We have added the sentence at the end of 4.2}

The new section 5 coincides more  or less with section 4 in the
SIGIR paper. Is "We therefore next investigate judge agreement"
still a useful  way of ending this section, given the inclusion of
a new research question?

\comment {We have deleted the offending sentence at the end of Section 5.}

Section 6:  ranges of scores for each worker involved was very wide
$\rightarrow$ RANGE of scores.

\comment {Fixed, thanks.}

Figure 7 has no legends (neither x nor y).

\comment {Curious: there are axis labels, and the symbols are explained
in the caption. Perhaps a printing error on the reviewer's side?}

What are the practical implications of the statement at the very
end of section 6, about the number of required workers? And what
does it say about setups where a smaller number of workers has been
used?

@@

Section 7 coincides with the old section 5. 
Figs 10, 11, 12 need legends.

\comment {Again, this seems fine on our copies.}

\comment {to do}

It would be good to explain the differences in absolute
numbers between Table IV in the TOIS submission and Table 2 in the
SIGIR paper. And why these differences do not matter.

\comment {We have added a sentence at the end of the first paragraph in Section 7.2 explaining the difference.}

### 2016-09-14 7_results_RQ3.tex
some small changes, and discovery of Section 7 disaster (which I did not fix)

Given that the agreement between our magnitude scores, TREC judgments
and Sormunen's judgments is not perfect, it is reasonable to expect
that relative system effectiveness orderings computed with each of
these as a basis may differ.
We first examine the correlation between system orderings using
magnitude estimation scores and TREC relevance as gain values, as for
both these judgment sets we have nearly complete coverage of the top 10
documents of all runs submitted to TREC-8, for our 18 judged topics.
% In the conference version of this paper~\cite{ME-SIGIR15} we showed the
% system scores (mean over all 18 topics) using median magnitude
% estimation scores per document (x-axis), and binary TREC categories
% (y-axis).
% This gave a result similar to Figure~\ref{fig:runs-rerank-median3best}.
% Unjudged documents were assumed to be irrelevant, as is common practice
% when using TREC data.
% \aht{What do you think of this almost self-referential style?}
% 
% Here we make a small alteration to the aggregation of the ME scores to
% get a single score for a document.
Rather than taking the median of all scores assigned to a document, we
take the median of scores taken from the three units that have document
orderings that have the highest agreement with the TREC orderings, or
Sormunen orderings, respectively.
In effect, the scores derived from units with high internal agreement as
computed in Section~\ref{sec:internal-agreement}, with ties broken in favor
of units with the least unjudged documents.
By aggregating scores over units that have a high agreement with the
original TREC orderings, any differences in system rankings we see should be more
attributable to the scale of the gain values, rather than perturbations in
document orderings given by different gain values.

@@

Table~\ref{tab:thin-med-thick} shows the correlation (Kendall's
$\tau$) between system orderings, and overlap of runs in the top set,
when using TREC and Sormunen judgments, and magnitude estimation
scores when the median is obtained from units that used a narrow scale,
a wide scale, or from all units (note that the $\tau$ values in the All
column match those in Figures~\ref{fig:runs-rerank-median3best}
and~\ref{fig:runs-rerank-median3best-fake}.
% \sm{false, taus are different now}
% \ref{fig:runs-rerank-median}
% and~\ref{fig:runs-rerank-median-fake}).
In each case the score for a topic-document pair is taken as 
the median of the 3 units that most agree with TREC or Sormunen 
and that are either narrow, wide or any as appropriate.
When there was no narrow or wide judgment for a topic-document pair
(all units containing that topic-document pair had
$\mbox{\hkh}/\mbox{\nkn}$ above or below the median), the median of the three best units was used.
This occurred in 12\% of TREC topic-document pairs, and 7\% of Sormunen topic-document pairs.
System orderings based on narrow or wide units show greater differences
(lower $\tau$ values) than when considering the full data set.
This is consistent with the results in Table~\ref{tab:scaling-cats}.
The overlap of the top set is generally less than 100\% for the
narrow/wide data sets, indicating that some perturbation of the set of
``equivalent'' top systems is occurring, but the pattern is not as clear as
for $\tau$ values.
This may be due to the relatively small number of topics that is being
considered, especially for the simulated systems, and more topics are
required before a definitive conclusion about the effect of narrow and
wide units on the top set can be made.

>>>>

Given that the agreement between our magnitude scores, TREC judgments
and Sormunen's judgments is not perfect, it is reasonable to expect
that relative system effectiveness orderings computed with each of
these as a basis may differ.
We first examine the correlation between system orderings using
magnitude estimation scores and TREC relevance as gain values, as for
both these judgment sets we have nearly complete coverage of the top 10
documents of all runs submitted to TREC-8, for our 18 judged topics.
% In the conference version of this paper~\cite{ME-SIGIR15} we showed the
% system scores (mean over all 18 topics) using median magnitude
% estimation scores per document (x-axis), and binary TREC categories
% (y-axis).
% This gave a result similar to Figure~\ref{fig:runs-rerank-median3best}.
% Unjudged documents were assumed to be irrelevant, as is common practice
% when using TREC data.
% \aht{What do you think of this almost self-referential style?}
% 
% Here we make a small alteration to the aggregation of the ME scores to
% get a single score for a document.
Rather than taking the median of all scores assigned to a document, we
take the median of scores taken from the three units that have document
orderings that have the highest agreement with the TREC orderings, or
Sormunen orderings, respectively.
In effect, the scores derived from units with high internal agreement as
computed in Section~\ref{sec:internal-agreement}, with ties broken in favor
of units with the least unjudged documents.
By aggregating scores over units that have a high agreement with the
original TREC orderings, any differences in system rankings we see should be more
attributable to the scale of the gain values, rather than perturbations in
document orderings given by different gain values.
\textcolor{red}{Note that this is a slightly less confounded methodology 
than was used in our previous paper~\cite{ME-SIGIR15}, which simply took the median 
of all units, and accounts for the 
differences between the figures and tables in this section and 
that previous paper.}

@@

Table~\ref{tab:thin-med-thick} shows the correlation (Kendall's
$\tau$) between system orderings, and overlap of runs in the top set,
when using TREC and Sormunen judgments, and magnitude estimation
scores when the median is obtained from units that used a narrow scale,
a wide scale, or from all units (note that the $\tau$ values in the All
column match those in Figures~\ref{fig:runs-rerank-median3best}
and~\ref{fig:runs-rerank-median3best-fake}).
% \sm{false, taus are different now}
% \ref{fig:runs-rerank-median}
% and~\ref{fig:runs-rerank-median-fake}).
In each case the score for a topic-document pair is taken as 
the median of the 3 units that most agree with TREC or Sormunen 
and that are either narrow, wide or any as appropriate.
When there was no narrow or wide judgment for a topic-document pair
(all units containing that topic-document pair had
$\mbox{\hkh}/\mbox{\nkn}$ above or below the median), the median of the three best units was used.
This occurred in 12\% of TREC topic-document pairs, and 7\% of Sormunen topic-document pairs.
\textcolor{green}{PANIC!!!!
System orderings based on narrow or wide units show greater differences
(lower $\tau$ values) than when considering the full data set.
This is consistent with the results in Table~\ref{tab:scaling-cats}.
The overlap of the top set is generally less than 100\% for the
narrow/wide data sets, indicating that some perturbation of the set of
``equivalent'' top systems is occurring, but the pattern is not as clear as
for $\tau$ values.
This may be due to the relatively small number of topics that is being
considered, especially for the simulated systems, and more topics are
required before a definitive conclusion about the effect of narrow and
wide units on the top set can be made.
}
